E Coli project paper

### 2013-07-12 paper/paper.tex

\begin{figure}
  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
  \caption{Pretty plot of the pair distribution function near a hard wall.}
  \label{fig:pair-distribution-3}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
  \caption{randst 99}
  %\label{}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
  \caption{randst 98}
  %\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
  \caption{randst 97}
  %\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
  \caption{randst 96}
  %\label{fig:pair-distribution-3}
\end{figure}
